---
title: "Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval = FALSE, include = FALSE}
knitr::opts_knit$set(root.dir = '..')
```

```{r setup}
library(fatalcaranalysiisreports)
knitr::opts_chunk$set(warning = TRUE)
```
## Introduction
This package graphically displays the locations of fatal accidents recorded in the US National Highway Traffic
Safety Administration's Fatal Analysis Reporting System (FARS). The function accepts a state number and year as parameters.

The lastest development version of the package can also be loaded directly from GitHub using the `devtools` package:

```{r eval = FALSE}
library(devtools)
install_github("gben1750/fatalcaranalysiisreports")
library(fatalcaranalysiisreports)
```
### Example
The grpahical display of accidents for Albama in the year 2013 can be shown in the following example.

*    fars_map_state (stateid, year)
``` {r example}
fars_map_state(1, 2013)
```
